---
title: "Index"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Module Project: PSY6422 Data Management & Visualization** 

## Introduction
<insert information about the background, my interest and what I want viewers to focus on and take away from the visualization> 

## Data Source 
<information about BRFSS 2018 – 2022> 

## Research Questions
1. Question 1
2. Question 2
3. Question 3
4. Question 4.

## Data Preparation & Validation 
Add head(rawfiles)
addhead(state changed)

I repeated the same process for the BRFSS2021, 2020, 2019 & 2018 files.>

<insert link for codebook–code + explanation > 

## Visualizaing the Code

#### Visualization 1
<insert explanation of question and background>
<cleaning the data – code + explanation >
<visualization>
<insert explanation of visualization> 

#### Visualization 2
<insert explanation of question and background>
<cleaning the data – code + explanation >
<visualization>
<insert explanation of visualization> 
gganimate::anim_save("Visualizations/contraceptive_animation.gif", animation = anim, width = 800, height = 600)

#### Visualization 3
<insert explanation of question and background>
<cleaning the data – code + explanation >
<visualization>
<insert explanation of visualization> 


#### Visualization 4
<insert explanation of question and background>
<cleaning the data – code + explanation >
<visualization>
<insert explanation of visualization> 

## Conclusion 
<Summary of what the project aimed to do>
<conclusions found with the analysed data>
<future considerations for project with the present data>
<What more can be done?>
<what I learnt>

## References
<data links 2018-2022>
```{r cars}
summary(cars)
```



You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
